---
title: "Data Vis Beastiary"
author: "ANLY 580"
date: "May 10, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

This assigment will help you familiarize yourself with the process of writing reproducible code and with sharing that code through a social portal such as GitHub.  

Your code is (theoretically) because the assignment was due last week.  Since then you were asked to setup a GitHub account.  Now you will use that account to add your code to this repo.  

Your tasks are:
- Fork the repo to your local machine
- Add your code below your name
- Add some description of the vis and the data set above your graphic
- Test your code on your local machine to verify execution
- Create a pull request to submit your code to the master branch

No doubt this will require some reading and thoughtful research on your part.  A great source of information can be found at http://kbroman.org/github_tutorial/




## Kevin Purcell (Instructor)

A *treemap* is a visual representation of a hierarchical (tree-like) dataset.  In which each branch of hierarchy is represented by rectangle.  The appearence of the treemap (size & color of rectangles) is scaled in relation to one or multiple varibles in the dataset.

Below is my example of a vis created with the `treemap` package using the `GNI2014` dataset, which is a listing of Gross Domestic Income in USD.


```{r, echo=TRUE}
library(treemap)   # Loading the treemap library
data(GNI2014)      # Included dataset on Gross National Income levels
treemap(GNI2014,                     # data frme
       index=c("continent", "iso3"), # a vector of aggregation indices from df
       vSize="population",           # identify the column that defines size
       vColor="GNI",                 # second vector to map to color
       type="value",                 # a type (7 choices)
       title="Gross National Income (per captia) in USD in 2014")
```


## Olayemi	Adejumo
## Isaac	Cyril

Below is my example with four box plots using the `iris` dataset, which gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica. 


```{r, echo=TRUE}

data("iris") #loading iris data
par(mfrow=c(2,2)) #Creating a matrix 2 rows and 2 columns
boxplot(iris$Sepal.Length,col="red") #Box plot of the sepal length in red
boxplot(iris$Sepal.Length~iris$Species,col="red") #Box plot of sepal length and species in red
boxplot(iris$Sepal.Length~iris$Species,col=heat.colors(3)) #Box plots with three heat colors
boxplot(iris$Sepal.Length~iris$Species,col=topo.colors(3)) #Box plots with three topo colors

```

## Ying	Dong
## Rui	Fan
## Sukanyaraj	Govindaraaj
## Kan	Hui
## Muhammad	Huzaifa
## Xinyi	Li
## Shen	Liu
## Vishwanath Kuma	Maharajapuram Ramachandran
## Jai	Rajora
## Yuanhui	Sui
## Shanfeng	Tang
## Russell	Taylor
## Gokul Krishna	Turaga
## Bongyong	Uh
## Xinting	Zhang
## Sicong	Zheng