---
title: "Data Vis Beastiary"
author: "ANLY 580"
date: "May 10, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

This assigment will help you familiarize yourself with the process of writing reproducible code and with sharing that code through a social portal such as GitHub.  

Your code is (theoretically) because the assignment was due last week.  Since then you were asked to setup a GitHub account.  Now you will use that account to add your code to this repo.  

Your tasks are:
- Fork the repo to your local machine
- Add your code below your name
- Add some description of the vis and the data set above your graphic
- Test your code on your local machine to verify execution
- Create a pull request to submit your code to the master branch

No doubt this will require some reading and thoughtful research on your part.  A great source of information can be found at http://kbroman.org/github_tutorial/




## Kevin Purcell (Instructor)

A *treemap* is a visual representation of a hierarchical (tree-like) dataset.  In which each branch of hierarchy is represented by rectangle.  The appearence of the treemap (size & color of rectangles) is scaled in relation to one or multiple varibles in the dataset.

Below is my example of a vis created with the `treemap` package using the `GNI2014` dataset, which is a listing of Gross Domestic Income in USD.


```{r, echo=TRUE}
library(treemap)   # Loading the treemap library
data(GNI2014)      # Included dataset on Gross National Income levels
treemap(GNI2014,                     # data frme
       index=c("continent", "iso3"), # a vector of aggregation indices from df
       vSize="population",           # identify the column that defines size
       vColor="GNI",                 # second vector to map to color
       type="value",                 # a type (7 choices)
       title="Gross National Income (per captia) in USD in 2014")
```


## Olayemi	Adejumo
## Isaac	Cyril
## Ying	Dong
## Rui	Fan
## Sukanyaraj	Govindaraaj
## Kan	Hui
## Muhammad	Huzaifa
## Xinyi	Li
## Shen	Liu
This is the example to use ggplot2, which is one decent tool in R to visualize the dataset. In following example, we use dataset airquality to explore the relationship between ozone content and temperature.
```{r,echo=TRUE}
   data11 <- data.frame(airquality) #get data
   ggplot(data11, aes(x = Temp, y = Ozone)) + #draw plot as Temp for independent variable and Ozone for dependent Var.
   geom_point(shape = 1) + #point shape
   geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black") +   #linear regression
   labs(x = "Temp", y = "Ozone") + #axis title
   ggtitle("Relationship Between Temp and Ozone") + #graph title
   theme_bw() 
```
## Vishwanath Kuma	Maharajapuram Ramachandran
## Jai	Rajora
## Yuanhui	Sui
## Shanfeng	Tang
## Russell	Taylor
## Gokul Krishna	Turaga
## Bongyong	Uh
## Xinting	Zhang
## Sicong	Zheng